Incentivizing Exploration with Unbiased History

### 2018-11-02 3level.tex
event 3

\xhdr{The ``good events".}
We establish four ``good events" each of which occurs with high probability.
\begin{description}
\item[(\event{1})] \emph{Exploration in Level 1:} Every first-level group collects at least $\Omega(T_1)$ samples of each arm.
\item[(\event{2})] \emph{Concentration in Level 1:} Within each first-level group, empirical mean rewards of each arm $a$ concentrate around $\mu_a$.
\item[(\event{3})] \emph{Anti-concentration in Level 1:} For each arm, some first-level subgroup collects data which makes this arm look much better than the other.
\item[(\event{4})] \emph{Concentration in prefix:}
The empirical mean reward of each arm $a$ concentrates around $\mu_a$ in any prefix of its pulls. (This ensures accurate reward estimates in exploitation.)
\end{description}

>>>>

\xhdr{The ``good events".}
We establish four ``good events" each of which occurs with high probability.
\begin{description}
\item[(\event{1})] \emph{Exploration in Level 1:} Every first-level group collects at least $\Omega(T_1)$ samples of each arm.
\item[(\event{2})] \emph{Concentration in Level 1:} Within each first-level group, empirical mean rewards of each arm $a$ concentrate around $\mu_a$.
\item[(\event{3})] \emph{Anti-concentration in Level 1:} For each arm, some first-level subgroup collects data which makes this arm look much better than its actual mean and other arms look worse than their actual means.
\item[(\event{4})] \emph{Concentration in prefix:}
The empirical mean reward of each arm $a$ concentrates around $\mu_a$ in any prefix of its pulls. (This ensures accurate reward estimates in exploitation.)
\end{description}
